---
title: |
  | Skeena Sockeye In Season Update
  | for SFNTC
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    
    fig_caption: yes
  html_notebook: default
geometry: "left=3cm,right=3cm,top=2cm,bottom=2cm"
editor_options:
  chunk_output_type: console
header-includes:
  - \usepackage{placeins}
  - \usepackage[justification=raggedright,labelfont=bf,singlelinecheck=false]{caption}
knit: (function(input, ...) {
      ),
      envir = globalenv()
    rmarkdown::render(
      input,
      output_file = paste0(
        xfun::sans_ext(input), '-', Sys.Date(), '.pdf'
---

------------------------------------------------------------------------

```{r setup options,echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE,echo=FALSE) 

```

```{r load libraries, include=FALSE}
library(tidyverse)
library(data.table)
library(readxl)
library(knitr)
library(ggpubr)

options(scipen=10000)
```

```{r loda data and format, include=FALSE}
data<-read_excel("data/tyee and catch and fence in-season updates 2023.xlsx",sheet="Tyee")
data$Date<-as.Date(data$Date)
```

```{r set days, echo=FALSE}
tyee.day<-as.Date("2023-06-26")
tyee.date<-"June 26"
fence.day<-as.Date("2023-06-26")
fence.date<-"June 26"
```

# Summary

- Early in the season. Sockeye are entering the Skeena with a cumulative total escapement of 56,905 to date

- Catchability coefficient in 2023 is 1307 sockeye per index point

\newpage

# Tyee Escapement and TRTC

```{r tyee table,echo=FALSE,results='asis'}
i<-match(tyee.day,data$Date)

average<-data$average[i]

e<-data$cumtyee[i]
t<-data$cumtrtc[i]
c<-data$cumcatch[i]

avgper<-round(data$Runtiming[i],3)*100
earlyper<-round(data$Runtiming[i+7],3)*100
lateper<-round(data$Runtiming[i-7],3)*100

#stat2<-data.frame(`Cumulative to Date`=c("Escapement Past Tyee","TRTC (Escapement+Catch)","Catch (preliminary"),`Number of Sockeye`=c(e,t,c))
#kable(stat2,caption=paste0("Cumulative escapement, TRTC, and catch to ",todate,"."))

stat3<-data.frame(`Cumulative to Date`=c("Escapement Past Tyee","TRTC (Escapement+Catch)","Catch (preliminary)"),`Number of Sockeye`=c(e,t,c),
                  `Run Timing`=c("Average","One week early","One week late"),`Percent Through`=c(avgper,earlyper,lateper))

kable(stat3,caption=paste0("Cumulative escapement, TRTC, and catch to ",tyee.date,"."))

```

```{r tyee plot setup, echo=FALSE,warning=FALSE}
escandtrtcdaily<-data%>%select(Date,Escapement=esctyee,TRTC=dailytrtc,`Average Escapement 85-21`=`ave85-21`)%>%
  pivot_longer(2:4,values_to="Number of Sockeye",names_to="Type")%>%
  mutate(lt=case_when(Type=="Escapement"|Type=="TRTC"~"2022",
                      Type=="Average Escapement 85-21"~"Average"))

t1<-ggplot(escandtrtcdaily,aes(x=Date,y=`Number of Sockeye`,color=Type,linetype=lt))+
  geom_line(size=1.1)+
  scale_color_manual(values=c("black","deepskyblue1","deepskyblue4"))+
  theme_classic()+
  grids(linetype = "dashed")+
  theme(legend.title = element_blank(),legend.position = "top")+
  guides(linetype="none")

escandtrtccum<-data%>%select(Date,Escapement=cumtyee,TRTC=cumtrtc,`Average Escapement 85-21`=`cum85-21`)%>%
  pivot_longer(2:4,values_to="Number of Sockeye",names_to="Type")%>%
  mutate(lt=case_when(Type=="Escapement"|Type=="TRTC"~"2022",
                      Type=="Average Escapement 85-21"~"Average"))

t2<-ggplot(escandtrtccum,aes(x=Date,y=`Number of Sockeye`,color=Type,linetype=lt))+
  geom_line(size=1.1)+
  scale_color_manual(values=c("black","deepskyblue1","deepskyblue4"))+
  theme_classic()+
  grids(linetype = "dashed")+
  theme(legend.title = element_blank(),legend.position = "top")+
  guides(linetype="none")
```

```{r tyee plots,fig.height=6,echo=FALSE,warning=FALSE,fig.cap="Daily (top) and cumulative (bottom) estimated escapement and TRTC (escapement + adjusted catch) at the Tyee test fishery versus the 1985-2021 average."}

ggarrange(t1,t2,align="v",ncol=1)

```

```{r,include=FALSE,fig.height=5,echo=FALSE,warning=FALSE,fig.cap="Cumulative estimated daily proportion of TRTC based on 1985-2021 average."}
pcum<-data%>%select(Date,cumtrtc,`Cumulative Proportion (85-21)`=`pcum85-21`)%>%
  mutate(`2023 Average Run Timing`=cumtrtc/average,
         `2023 Late Run Timing`=cumtrtc/late,
         `2023 Early Run Timing`=cumtrtc/early)%>%
  select(-cumtrtc)%>%
  pivot_longer(2:5,names_to="Type",values_to="Cumulative Proportion")%>%
  mutate(Type=factor(Type,levels=c("2023 Early Run Timing","2023 Average Run Timing","2023 Late Run Timing","Cumulative Proportion (85-21)")))

ggplot(pcum,aes(x=Date,y=`Cumulative Proportion`,color=Type,linetype=Type))+
  geom_line(size=1.1)+
  scale_colour_manual(values=c("green","deepskyblue2","pink","black"))+
  scale_linetype_manual(values=c("solid","solid","solid","dashed"))+
  theme_classic()+
  grids(linetype = "dashed")+
  theme(legend.title=element_blank(),legend.position=c(.8,.2),legend.background = element_blank())
```

\newpage

# Tyee run-timing model

```{r tyee model table,echo=FALSE,results='asis'}

i<-match(tyee.day,data$Date)

early<-data$early[i]
average<-data$average[i]
late<-data$late[i]

stat1<-data.frame(`Run-Timing`=c("Early","Average","Late"),`Forecasted Final Run Size`=c(early,average,late))

kable(stat1,caption="Forecasted sockeye final TRTC based on early, average and late run-timing.")

```

```{r tyee model figure,fig.height=4,echo=FALSE,warning=FALSE,fig.cap="Forecasted final TRTC of Skeena sockeye based on the simple scalar run-timing model."}
tyeemodel<-data%>%select(Date,Early=early,Average=average,Late=late)%>%
  pivot_longer(2:4,values_to="Number of Sockeye",names_to="Timing")

ggplot(tyeemodel,aes(x=Date,y=`Number of Sockeye`,color=Timing))+
  geom_line(size=1.5)+
  scale_color_brewer(palette="Set1")+
  theme_classic()+
  grids(linetype = "dashed")+
  theme(legend.position = "top")
```

```{=tex}
\FloatBarrier
\newpage
```
# Babine Fence

```{r load fence data,echo=FALSE,results='asis'}
fence<-read_excel("tyee and catch and fence in-season updates.xlsx",sheet="Babine")
fence$Date<-as.Date(fence$Date)
```

```{r fence summary table,echo=FALSE,results='asis'}
i<-match(fence.day,fence$Date)

totalrun<-fence$cumrun[i]
cumjacks<-fence$cumjacks[i]

stat2<-data.frame(`Babine Fence`=c("Large Sockeye","Jacks"),`Total Run`=c(totalrun,cumjacks))

kable(stat2,caption=paste0("Cumulative large sockeye and jacks to Babine River fence to ",fence.date,"."))

```

\FloatBarrier

```{r fence plots,echo=FALSE,warning=FALSE}
  
fencedaily<-fence%>%select(Date,`2022 Total Run`=totalrun,`2014 Total Run`=`2014`,`Average 2011-2021`=`avg11-21`)%>%
  pivot_longer(2:4,values_to="Number of Sockeye",names_to="Type")%>%
  mutate(lt=case_when(Type=="2022 Total Run"|Type=="2014 Total Run"~"Annual",
                      Type=="Average 2011-2021"~"Average"))

b1<-ggplot(fencedaily,aes(x=Date,y=`Number of Sockeye`,color=Type,linetype=lt))+
  geom_line(size=1.1)+
  scale_color_manual(values=c("grey50","deepskyblue3","black"))+
  theme_classic()+
  grids(linetype = "dashed")+
  theme(legend.title = element_blank(),legend.position = "top")+
  guides(linetype="none")+
  labs(y="# of Large Sockeye")

fencecum<-fence%>%select(Date,`2022 Total Run`=cumrun,`Average 2011-2021`=`cumavg11-21`,`2014 Total Run`=cum2014)%>%
  pivot_longer(2:4,values_to="Number of Sockeye",names_to="Type")%>%
  mutate(lt=case_when(Type=="2022 Total Run"|Type=="2014 Total Run"~"Annual",
                      Type=="Average 2011-2021"~"Average"))

b2<-ggplot(fencecum,aes(x=Date,y=`Number of Sockeye`,color=Type,linetype=lt))+
  geom_line(size=1.1)+
  scale_color_manual(values=c("grey50","deepskyblue3","black"))+
  theme_classic()+
  grids(linetype = "dashed")+
  theme(legend.title = element_blank(),legend.position = "top")+
  guides(linetype="none")

```

```{r combined fence plot,fig.height=6,echo=FALSE,warning=FALSE,fig.cap="Top panel: Total run to Babine fence for 2022 compared to 2014 (recent highest year) and the average from 2011-2021. Bottom panel: Cumulative estimated run to the Babine fence for 2022, 2014 (recent highest year) and the average from 2011-2021."}

ggarrange(b1,b2,ncol=1,align="v",common.legend = TRUE)

```

\newpage

# Babine comparison with Tyee

This comparison aims to provide an idea on the catchability at Tyee. The red line in the figure below shows the difference between the escapement past Tyee and the total run being counted at the Babine Fence, based on some assumptions. These assumptions include 3 week migration timing, 10% non-Babine stock composition and \~ 40,000 of harvest between Tyee and Babine.

```{r,echo=FALSE,fig.height=6,fig.cap="Estimated difference in sockeye between escapement past Tyee and the Babine Fence based on 3 week migration timing, 10% non-Babine stocks, and ~ 40,000 catch between Tyee and Babine spread over 2-3 weeks."}

pernonbabine<-.1

ty<-data%>%select(Date, Observed.Tyee=cumtyee)
fe<-fence%>%select(Date,Actual.Fence=cumrun)

inrivercatch<-read_excel("tyee and catch and fence in-season updates.xlsx",sheet="inriver catch")
inrivercatch$Date<-as.Date(inrivercatch$Date)

ca<-inrivercatch%>%select(Date,totalfromfence)

comp<-merge(ty,fe,all=TRUE)%>%merge(ca,all=TRUE)%>%
  mutate(Expected.Babine=lag((1-pernonbabine)*Observed.Tyee,21),
         `Difference @ 3 Weeks`=Actual.Fence-Expected.Babine-totalfromfence)%>%
  select(-totalfromfence)%>%
  pivot_longer(2:5,names_to="Count",values_to="Fish")

ggplot(comp,aes(x=Date,y=Fish,color=Count,size=Count,linetype=Count))+
  geom_line()+
  theme_classic()+grids()+
  scale_colour_manual(values=c("black","red","seagreen4","blue"))+
  scale_linetype_manual(values=c("solid","solid","dashed","solid"))+
  scale_size_manual(values=c(2,1,1,1.5))+
  theme(legend.position="top")+
  labs(y="Number of Large Sockeye")+
  ylim(-1000000,3500000)

```

\newpage

# Babine Sockeye Jacks

```{r fence jacks, echo=FALSE,warning=FALSE}
fencejacks<-fence%>%select(Date,jacks=dailytotaljacks,`jack90-21`)%>%
  pivot_longer(2:3,values_to="Number of Sockeye",names_to="Type")%>%
  mutate(lt=case_when(Type=="jacks"~"Annual",
                      Type=="jack90-21"~"Average"))

j1<-ggplot(fencejacks,aes(x=Date,y=`Number of Sockeye`,color=Type,linetype=lt))+
  geom_line(size=1.1)+
  scale_color_manual(values=c("grey50","deepskyblue3","black"))+
  theme_classic()+grids()+
  theme(legend.title = element_blank(),legend.position = "top")+
  guides(linetype="none")+
  labs(y="# of Large Sockeye")

jackscum<-fence%>%select(Date,cumjacks,`cumjack90-21`)%>%
  pivot_longer(2:3,values_to="Number of Sockeye",names_to="Type")%>%
  mutate(lt=case_when(Type=="cumjacks"~"Annual",
                      Type=="cumjack90-21"~"Average"))

j2<-ggplot(jackscum,aes(x=Date,y=`Number of Sockeye`,color=Type,linetype=lt))+
  geom_line(size=1.1)+
  scale_color_manual(values=c("grey50","deepskyblue3","black"))+
  theme_classic()+grids()+
  theme(legend.title = element_blank(),legend.position = "top")+
  guides(linetype="none")

```

```{r babine jack plots,fig.height=6,echo=FALSE,warning=FALSE,fig.cap="Daily (top) and cumulative (bottom) estimated total run of sockeye jacks at the Babine Fence versus the 1990-2021 average."}

ggarrange(j1,j2,align="v",ncol=1)

```

```{r hcr,echo=FALSE,warning=FALSE}

hcr<-data.frame(TRTC=c(0,1050000,2000000,4000000,5000000),
                HR=c(0,0,.2,.4,.4))

p1<-ggplot(hcr,aes(x=TRTC/10^6,y=HR))+
  geom_line(size=1.1)+
  geom_vline(xintercept=average/10^6,linetype="dashed",col="red")+
  theme_classic()+
  ylim(0,1)+
  grids(linetype = "dashed")+
  labs(y="Canadian Harvest Rate",x="Skeena sockeye return to Canada (millions)")

data<-data%>%rowwise()%>%mutate(TAC=case_when(average<1050000~0,
                          average>=1050000&average<2000000~((average-1050000)/(2000000-1050000)*(.2-.0)+0)*average,
                          average>=2000000&average<4000000~((average-2000000)/(4000000-2000000)*(.4-.2)+.2)*average,
                          average>=4000000~.4*average))

ggcatch<-data%>%select(Date,`Cumulative Comm. Catch`=cumcatch,`Total Allowable Catch`=TAC)%>%
  pivot_longer(2:3,names_to="Catch Type",values_to="Catch")%>%
  filter(Date>"2022-07-01"&Date<"2022-08-15")

p2<-ggplot(ggcatch,aes(x=Date,y=Catch,Catch,color=`Catch Type`,size=`Catch Type`))+
  geom_line(size=1.1)+
  scale_color_manual(values=c("deepskyblue3","black"))+
  scale_size_manual(values=c(2,1))+
  #scale_linetype_manual(values=c("solid","dashed"))+
  theme_classic()+
  grids(linetype = "dashed")+
  labs(y="Cumulative\nSockeye Catch")+
  theme(legend.position="top")

catch<-data%>%select(Date,Gillnet=gncatch,Seine=sncatch)%>%
  pivot_longer(2:3,names_to="Gear",values_to="Catch")%>%
    filter(Date>"2022-07-01"&Date<"2022-08-15")

p3<-ggplot(catch,aes(x=Date,y=Catch,fill=Gear))+
  geom_col()+
  scale_fill_brewer(palette="Set1")+
  theme_classic()+
  grids(linetype = "dashed")+
  theme(legend.position="top")

cpue<-data%>%select(Date,gncatch,sncatch,gneffort,sneffort)%>%
  mutate(Gillnet=gncatch/gneffort,Seine=sncatch/sneffort)%>%
  select(Date,Gillnet,Seine)%>%
  pivot_longer(2:3,names_to="Gear",values_to="CPUE")%>%
  filter(Date>"2022-07-01"&Date<"2022-08-15")

p4<-ggplot(cpue,aes(x=Date,y=CPUE,color=Gear))+
  geom_line()+geom_point()+
  scale_color_brewer(palette="Set1")+
  theme_classic()+
  grids(linetype="dashed")+
  theme(legend.position = "top")

```

```{=tex}
\FloatBarrier
\newpage
```
# Area 4 Commercial Marine Catch

```{r,fig.height=6,echo=FALSE,warning=FALSE,fig.cap="Top panel: The Skeena sockeye harvest control rule based on TRTC. Bottom panel: Cumulative Area 4 gillnet and seine sockeye catch versus daily estimates of TAC based on average run-timing in-season TRTC model."}

ggarrange(p1,p2,ncol=1,align="v")
```

\newpage

```{r,fig.height=6,echo=FALSE,warning=FALSE,fig.cap="Top panel: Area 4 gillnet and seine sockeye catch. Bottom panel: CPUE of gillnet and seine based on daily catch/daily effort. Note that some values are preliminary."}

ggarrange(p3,p4,ncol=1,align="v")


```

\newpage

# Stock Specific Run-timing

This shows an example of what stock specific run-timings might look like versus the aggreagete based on average run-timing from the 2018 English et. al. run-timing report. Note that the updated run-timing information that Karl provided from the NBRR updates is not included yet.

```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.height=4}
agg<-fread("aggregate tyee run timing.csv")

RT<-data.frame(Date=seq(as.Date("2022-06-10"),as.Date("2022-09-01"),1))%>%
  mutate(julian=as.numeric(format(Date, "%j")))%>%
  mutate(morice=dnorm(julian,196.5,14),
         kitwanga=dnorm(julian,210.5,15.7),
         babineriver=dnorm(julian,217.5,12.5))%>%
  merge(agg)%>%
  pivot_longer(3:6,names_to="Stock",values_to="RT")%>%
  mutate(type=ifelse(Stock=="agg85-21","Aggregate","Stock"))

#ggplot(RT,aes(x=Date,y=RT,color=Stock,linetype=type))+
#  geom_line(size=1.1)+
#  theme_classic()+
#  scale_linetype_manual(values=c("dashed","solid"))+
#  scale_color_manual(values=c("black","red","green3","blue"))+
#  grids(linetype="dashed")+
#  theme(legend.position = "top")+
#  guides(linetype="none")

RT2<-RT%>%filter(Stock!="agg85-21")

```

```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.height=4,fig.cap="Estimated average run-timing of Morice, Kitwanga and Babine River sockeye versus the average aggregate run-timing at Tyee."}
ggplot()+
  geom_line(data=RT2,aes(x=Date,y=RT,color=Stock),size=1.1)+
  geom_line(data=agg,aes(x=Date,y=`agg85-21`),linetype="dashed",size=1.2)+
  theme_classic()+
  scale_linetype_manual(values=c("dashed","solid"))+
  grids(linetype="dashed")+
  theme(legend.position = "top")+
  labs(y="Daily proportion")
```

```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.height=4}
hrs<-read_excel("Skeena Stock ER calculator-DRAFT-2022.xlsx",sheet="HRs for R")

hr2<-hrs%>%select(!"Aggregate Weekly")%>%pivot_longer(2:5,names_to="stock",values_to="Weekly HR")

h1<-ggplot(hrs,aes(x=`Week End`,y=`Aggregate Weekly`))+
  geom_point(color="red")+geom_line(color="#E41A1C")+
  scale_color_brewer(palette="Set1")+
  theme_classic()+grids()+
  theme(legend.position = "top",axis.text.x=element_blank(),axis.title.x = element_blank())+
  labs(y="Aggregate Weekly HR")
  
h2<-ggplot(hr2,aes(x=`Week End`,y=`Weekly HR`,color=stock))+
  geom_point()+geom_line()+
  scale_color_brewer(palette="Set1")+
  theme_classic()+grids()+
  theme(legend.position = "top",axis.text.x=element_blank(),axis.title.x = element_blank())+
  labs(y="Stock HR by week")

hr3<-hr2%>%group_by(stock)%>%mutate(cum=cumsum(`Weekly HR`))

h3<-ggplot(hr3,aes(x=`Week End`,y=cum,color=stock))+
  geom_point()+geom_line()+
  scale_color_brewer(palette="Set1")+
  theme_classic()+grids()+
  theme(legend.position = "top")+
  labs(y="Cumulative stock HR by week")

```

\newpage

# Stock specific estimated harvest rates.

\*Based on late aggregate and stock run-timing, and MEDIUM stock length (e.g. shorter run-timing versus the average).

```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.height=6,fig.cap="Weekly harvest rates on the aggregate (top), and harvest rates by week (middle) and cumulative (bottom) for Morice, Kitwanga and Babine River sockeye. Note this is basse on MEDIUM duration and late timed stock runs."}

ggarrange(h1,h2,h3,ncol=1,align='v',common.legend = TRUE)

```

\newpage

# Appendix A-Pink, chum, coho, chinook and steelhead

```{r other species catch,fig.height=7,echo=FALSE,message=FALSE,warning=FALSE,fig.cap="Number of other species caught and released (coho, chinook, chum and steelhead), or kept (pinks)."}
othercatch<-read_excel("tyee and catch and fence in-season updates.xlsx",sheet="gncatch")

oc2<-othercatch%>%pivot_longer(4:8,names_to="Species",values_to="Catch")%>%
  mutate(cpue=Catch/effort)%>%
  filter(Date>as.Date("2022-07-10")&Date<as.Date("2022-08-10"))%>%
  mutate(type=ifelse(Species%in%c("Chinook (Released)","Chum (Released)","Steelhead (Released)","Coho (Released)"),"Released","Kept"))%>%
  mutate(sp=case_when(Species=="Chinook (Released)"~"Chinook",
                      Species=="Coho (Released)"~"Coho",
                      Species=="Pink (Kept)"~"Pink Kept",
                      Species=="Pink (Released)"~"Pink Rel",
                      Species=="Chum (Released)"~"Chum",
                      Species=="Steelhead (Released)"~"Steelhead"))

ggplot(oc2,aes(x=Date,y=Catch,color=gear))+
  geom_line()+geom_point()+
  theme_classic()+
  grids()+
  facet_wrap(~Species,ncol=2,scales="free_y")+
  theme(legend.position="top")
```

\newpage

```{r other species catch2,fig.height=7,echo=FALSE,message=FALSE,warning=FALSE,fig.cap="Number of other species caught and released (coho, chinook, chum and steelhead), or kept (pinks)."}
ggplot(oc2,aes(x=Date,y=Catch,fill=gear))+
  geom_col(position="dodge")+
  theme_classic()+
  grids()+
  facet_wrap(~Species,ncol=2,scales="free_y")+
  theme(legend.position="top")


```

\newpage

```{r other species seine cpue,fig.height=7,echo=FALSE,message=FALSE,warning=FALSE,fig.cap="CPUE of other species caught and released (coho, chinook, chum and steelhead), or kept (pinks), by SEINES."}

sncpue<-oc2%>%filter(gear=="seine")

ggplot(sncpue,aes(x=Date,y=cpue))+
  geom_line()+geom_point()+
  theme_classic()+
  grids()+
  facet_wrap(~Species,ncol=2,scales="free_y")+
  theme(legend.position="top")
```

\newpage

```{r other species gillnet cpue,fig.height=7,echo=FALSE,message=FALSE,warning=FALSE,fig.cap="CPUE of other species caught and released (coho, chinook, chum and steelhead), or kept (pinks) by GILLNETS."}
gncpue<-oc2%>%filter(gear=="gillnet")

ggplot(gncpue,aes(x=Date,y=cpue))+
  geom_line()+geom_point()+
  theme_classic()+
  grids()+
  facet_wrap(~Species,ncol=2,scales="free_y")+
  theme(legend.position="top")
```

```{=tex}
\FloatBarrier
\newpage
```
```{r other species total catch by gear,fig.height=6,echo=FALSE,message=FALSE,warning=FALSE,fig.cap="CPUE of other species caught and released (coho, chinook, chum and steelhead), or kept (pinks) by gillnets and seines in marine Area 4 commercial fishery."}

oc.total<-oc2%>%group_by(gear,Species=sp,type)%>%summarise(total=sum(Catch,na.rm=TRUE))

oc.table<-oc.total%>%pivot_wider(names_from=c("gear","type"),values_from="total")%>%replace(is.na(.),0)

kable(oc.table,caption=paste0("Total catch of coho, chum, chinook, pink and steelhead in the commercial gillent and seine fisheries to ",tyee.date,"."))

ggplot(oc.total,aes(x=Species,y=total,fill=gear))+
  geom_col()+
  facet_wrap(~type,ncol=1,scales="free_y")+
  theme_classic()+grids()+
  labs(y="Total Catch",x="Species")+
  theme(strip.background = element_blank())

```

\newpage

# Population specific run-timing through Tyee

Notes:

-   Based on NBRR update data (2000-2014) provided by Karl English July 2022. Will add in the newer data and some comparisons.

-   These are average run-timings. Explorations on the differences between the average and ANNUAL run-timing standard deviations are underway for stocks with appropriate sample size.

```{r,echo=FALSE,include=FALSE,warning=FALSE,message=FALSE}
setwd("C:/Users/Andy1/Documents/R/Skeena/Sockeye")

rt<-read_excel("rt karl.xlsx",sheet="Sheet1")

n=10000

rtm<-data.frame()

for (i in 1:nrow(rt)){
  u<-rt$MeanJulian[i]
  sd<-rt$SD[i]
  
  g<-data.frame(stock=rt$Stock[i],dev=rnorm(n,rt$MeanJulian[i],rt$SD[i]))
  rtm<-rbind(rtm,g)
  
}

#as.numeric(format(as.Date("2022-08-07"), "%j"))

days<-format(seq(as.Date("2022-06-01"),as.Date("2022-09-15"),10),"%b-%d")

rtm2<-rtm%>%filter(dev>=152&dev<=258)%>%group_by(stock)%>%mutate(u=mean(dev))

```

\FloatBarrier

```{r,echo=FALSE,fig.cap="Boxplots of stock specific run-timing through Tyee. Based on 2000-2014 data provided by karl English from updated NBRR work. The filled area of the box represents 50% of the run." ,fig.height=8,warning=FALSE,message=FALSE}

ggplot(rtm2,aes(x=dev,y=reorder(stock,dev,FUN=median),fill=stock))+
  geom_boxplot()+
  theme_classic()+grids()+
  scale_y_discrete(limits=rev)+
  guides(fill="none")+
  labs(y="Stock",x="Date",title="Stock run-timing at Tyee based on 2000-2014 GSI",subtitle="NBRR data provided by Karl English July 2022")+
 scale_x_continuous(breaks=seq(152,258,10),labels=days)+
  theme(axis.text.x = element_text(angle=90))

```

\newpage

```{r,echo=FALSE,fig.cap="Histograms of stock specific run-timing through Tyee. Based on 2000-2014 data provided by karl English from updated NBRR work.",fig.height=8,warning=FALSE,message=FALSE}
ggplot(rtm2,aes(x=dev))+
  geom_histogram(aes(fill=stock),binwidth = 5,alpha=.3)+
  facet_grid(reorder(stock,dev,FUN=median)~.,scales="free_y",switch="y")+
  theme_classic()+grids()+
  theme(strip.text.y.left = element_text(angle=0,size=8),
        strip.placement="outside",
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        strip.background = element_blank(),
        axis.text.x = element_text(angle=90))+
  labs(y="Stock",x="Date",title="Stock run-timing at Tyee based on 2000-2014 GSI",subtitle="NBRR data provided by Karl English July 2022")+
  geom_vline(aes(xintercept=u,color=stock), size=1,alpha=.5)+
  scale_x_continuous(breaks=seq(152,258,10),labels=days)+
  guides(fill="none",color="none")+
  annotate("rect", xmin = 196, xmax = 219, ymin = 0, ymax = Inf,alpha = .2)
  
```

\newpage

```{r,echo=FALSE,fig.cap="Density plot of stock specific run-timing through Tyee. Based on 2000-2014 data provided by karl English from updated NBRR work.",fig.height=8,warning=FALSE,message=FALSE}
ggplot(rtm2,aes(x=dev),color=stock)+
  geom_density(aes(fill=stock),alpha=.3)+
  #scale_fill_brewer(palette="Set1")+
  facet_wrap(~reorder(stock,dev,FUN=median),scales="free_y",ncol=1,strip.position="left")+
  theme_classic()+grids()+
   theme(strip.text.y.left = element_text(angle=0,size=8),
        strip.placement="outside",
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        axis.ticks.x=element_blank(),
        strip.background = element_blank(),
        axis.text.x = element_text(angle=90),
        plot.caption.position="plot",
        plot.caption=element_text(hjust=.5))+
  geom_vline(aes(xintercept=u,color=stock), size=1,alpha=.5)+
  labs(y="Stock",x="Date",caption="Stock run-timing at Tyee based on average run-timing (2000-2014) plus 3 weeks.\nVertical lines show the mean for each stock, with the 2022 harvest window\nshown by the grey shaded box.\nData from Karl English from NBRR update provided July 2022.")+
  scale_x_continuous(breaks=seq(152,258,10),labels=days)+
  guides(fill="none",color="none")+
   annotate("rect", xmin = 196, xmax = 219, ymin = 0, ymax = Inf,alpha = .2)

#ggsave("Tyee stock run timing.png",dpi=600,height=8,width=7)
```

```{r babine run timing stocks,include=FALSE}
babrt<-rtm%>%filter(stock%in%c("Babine W Early","Babine W Middle","Babine W Late","Babine Pinkut","Babine Fulton"))%>%
  mutate(fencert=dev+21)

days<-format(seq(as.Date("2022-07-01"),as.Date("2022-10-07"),7),"%b-%d")
as.numeric(format(as.Date("2022-10-07"), "%j"))

babrt2<-babrt%>%filter(fencert>=182&fencert<=280)%>%group_by(stock)%>%mutate(med=mean(fencert))

babmed<-babrt%>%group_by(stock)%>%summarise(u=mean(fencert))

ggplot(babrt2,aes(x=fencert))+
  geom_density(aes(fill=stock),alpha=.3)+
  scale_fill_brewer(palette="Set1")+
  facet_wrap(~reorder(stock,dev,FUN=median),scales="free_y",ncol=1,strip.position="left")+
  theme_classic()+grids()+
  theme(strip.text.y.left = element_text(angle=0,size=8),
        strip.placement="outside",
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        axis.ticks.x=element_blank(),
        strip.background = element_blank(),
        axis.text.x = element_text(angle=90),
        plot.caption.position="plot",
        plot.caption=element_text(hjust=0))+
  geom_vline(aes(xintercept =med,color=stock), size=1,alpha=.5)+
  scale_color_brewer(palette="Set1")+
  labs(y="Stock",x="Date",
  caption="Stock run-timing at Babine fence based on average Tyee run-timing (2000-2014) plus 3 weeks.\nData from Karl English from NBRR update provied July 2022.")+
  scale_x_continuous(breaks=seq(182,280,7),labels=days)+
  guides(fill="none",color="none")

#ggsave("Babine run timing for Donna.png",dpi=600,height=8,width=7)
```
